### 2022-10-19 draft/draft.Rmd
almost done

```{r mbconnectome-ase, fig.cap = 'ASE of the Drosophila connectome graph. The embedding vectors are labeled by neuron type.', fig.height = 2, figh.width = 4}
Xhat <- embedding(A, 2, 0)

ggplot() + 
  geom_point(aes(x = Xhat[, 1], y = Xhat[, 2],
                 colour = factor(z))) + 
  coord_fixed() +
  theme_bw() + 
  scale_colour_brewer(palette = 'Set1') + 
  labs(x = expression(x[1]), y = expression(x[2]),
       colour = NULL)
```

```{r mbconnectome-kcurves, fig.cap = 'ASE of the Drosophila connectome graph with quadratic Bezier curves fitted via $K$-curves clustering. The embedding vectors are colored by predicted label.', fig.height = 2, fig.width = 4, cache = TRUE}
set.seed(314159)
z.init <- sample.points(z, 3)

@@

plot.estimated.curves(Xhat, mbconnectome.out) + 
  scale_colour_brewer(palette = 'Set1') + 
  # coord_fixed(.5) + 
  labs(x = expression(x[1]), y = expression(x[2]))
```

@@

>>>>

```{r mbconnectome-ase, fig.cap = 'ASE of the Drosophila connectome graph. The embedding vectors are labeled by neuron type.', fig.height = 2, fig.width = 8}
Xhat <- embedding(A, 2, 0)

ggplot() + 
  geom_point(aes(x = Xhat[, 1], y = Xhat[, 2],
                 colour = factor(z))) + 
  coord_fixed(.5) +
  theme_bw() + 
  theme(legend.position = 'none') +
  scale_colour_brewer(palette = 'Set1') + 
  labs(x = expression(x[1]), y = expression(x[2]),
       colour = NULL)
```

```{r mbconnectome-kcurves, fig.cap = 'ASE of the Drosophila connectome graph with quadratic Bezier curves fitted via $K$-curves clustering. The embedding vectors are colored by predicted label.', fig.height = 2, fig.width = 8, cache = TRUE}
set.seed(314159)
z.init <- sample.points(z, 3)

@@

plot.estimated.curves(Xhat, mbconnectome.out) + 
  scale_colour_brewer(palette = 'Set1') + 
  coord_fixed(.5) +
  labs(x = expression(x[1]), y = expression(x[2]))
```

@@

\begin{proof}[Proof of theorem \ref{thm:kcurves-semisupervised}]
\end{proof}
